Ce que j'ai compris jusqu'à maintenant\\Début de rapport ?

### 2025-03-31 article_bihom_v2.tex
fin du début de la partie sur GB

% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage[backend=bibtex]{biblatex}
\usepackage{csquotes}
\addbibresource{biblio.bib}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Définition}[section]
\newtheorem{theoreme}{Théorème}[section]

@@

		The major "issue" of Gröbner basis algorithms is the reductions to 0, because of the matrices sizes that are huge, multiple millions for practical examples,
		reductions to 0 can cost a lot during the linear algebra process. F5 \cite{F02} was a major improvement because it provided a criterion that avoided reduction to 0 during the linear algebra part for all regular sequences.
		Bardet showed in \cite{Bardet04} that F5 criterion removed reductions to 0 for semi-regular sequences until the degree $d = H(I) -1$ where $I$ is the ideal generated by the polynomial sequence and $H(I)$ is the index of regularity of the ideal $I$.

>>>>

% !TXS template
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper]{geometry}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage[backend=bibtex]{biblatex}
\usepackage{csquotes}
\addbibresource{biblio.bib}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]

@@

		The major "issue" of Gröbner basis algorithms is the reductions to 0, because of the matrices sizes that are huge, multiple millions for practical examples,
		reductions to 0 can cost a lot during the linear algebra process. F5 \cite{F02} was a major improvement because it provided a criterion that avoided reduction to 0 during the linear algebra part for all regular sequences.
		Bardet showed in \cite{Bardet04} that F5 criterion removed reductions to 0 for semi-regular sequences until the degree $D$ which is the degree of regularity of $I$.

		According to \cite{BFS15}, the complexity of computing the Gröbner basis of a system $f_1,...,f_m \in \mathbb{K}[x_1,...,x_n]$ is $O(mD\binom{n+D-1}{D}^\omega)$.

		In \cite{Bardet04} Theorem 3.2.10 is the following

		\begin{theorem}
			Let $f_1,...,f_m$ homogeneous sequence, such that $<f_1,...,f_m>$ is 0-dimensional and
			$<$ an admissible graded monomial ordering. We have,
			\begin{itemize}
				\item[-] If the sequence is semi-regular, then no reductions to 0 are performed during the F5-matrix algorithm until the degree of regularity $D - 1$.
				\item[-] If there is no reductions to 0 during the F5-matrix algorithm until the degree $D - 1$, and if the matrix of degree D is full rank and is the first matrix to have more rows than columns, then the sequence is semi-regular and it's index of regularity is $H(I) = D$.
			\end{itemize}
		\end{theorem}

		However, after some tests and after applying F5-matrix algorithm on polynomial systems generated by NSBC instances, we get reductions to 0, this means that the polynomial systems are not semi-regular.

		\subsection{Bilinear systems case}
